---
title: 'Mortatlity in TBM based baseline gene expression '
author: "Haiht"
date: '2023-03-31'
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

# Set up R enviroment {.tabset .tabset-fade .tabset-pills}
Set the random generator seed so we can reproduce exactly results without any stochasticity

```{r setup, message=FALSE, warning=FALSE, echo= FALSE, results='hide'}
knitr::opts_chunk$set(
	fig.height = 6,
	fig.width = 8,
	message = FALSE,
	warning = FALSE
	)

 # Set the random generator seed so we can reproduce exactly results without any stochasticity
#rm(list=ls())
set.seed(1235)
```


```{r}
library(ggplot2)
library(WGCNA)
library(Hmisc)
library(dplyr)
library(magrittr)
library(caret)
source("../R_functions/WGCNA_CEMitool_Allfunctions_5May2022.R")
#source("../R_functions/WGCNA_CEMitool_Allfunctions_5May2022.R")
```

# 1. Load input data

```{r}
## set multi threads
enableWGCNAThreads(nThreads=12)
# Load the data saved in the first part
output <- "WGCNA/All_study/Consensus_TBM/Discovery_validation_Dex_HIV/"
study = "TBM_Death_281"
lnames = load( paste0(output,"RData/",study,"-01-dataInput.RData"));
# The variable lnames contains the names of loaded variables.
lnames

# Get the number of sets in the multiExpr structure.
dim(multiExpr[[1]]$data)
nSets = checkSets(multiExpr)$nSets
```

# 2. Pick softthreshold

```{r}
# Choose a set of soft-thresholding powers
powers = c(1:20);
# Call the network topology analysis function
sft = pickSoftThreshold(multiExpr[[1]]$data, powerVector = powers, verbose = 5)
# Plot the results:
sizeGrWindow(9, 5)
jpeg(file = paste0(output_figures,study_dis,"-scaleFreeAnalysis.jpeg"), wi = 9, he = 5,
    units = 'in',res = 300)
par(mfrow = c(1,2));
cex1 = 0.85;
# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.9,col="red")
# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")

dev.off();
sft$fitIndices[,5][8:15]
```
# 3. Construct network

```{r}
power=sft$powerEstimate
#(with mean conectivity = 14.993420)
net_dis = blockwiseModules(multiExpr[[1]]$data, power = power,
                       maxBlockSize = 5000,
                       networkType="unsigned",
                       TOMType = "signed", minModuleSize = 30,
                       reassignThreshold = 0, mergeCutHeight = 0.3,
                       numericLabels = TRUE, pamRespectsDendro = FALSE,
                       saveTOMs = TRUE,
                       saveTOMFileBase = paste0(output,"RData/",study_dis,"-TOM_5000"), 
                       verbose = 3)
```

# 4.Plot dendrogram network

```{r}
# open a graphics window
mergedColors = labels2colors(net_dis$colors)
jpeg(file = paste0(output_figures,study_dis,"_Dendrogram-auto.jpeg"), wi = 12, he = 9,units = 'in', res = 480)
sizeGrWindow(12, 9)
plotDendroAndColors(net_dis$dendrograms[[1]], mergedColors[net_dis$blockGenes[[1]]],
                    "Module colors",
                    dendroLabels = FALSE, hang = 0.03,
                    addGuide = TRUE, guideHang = 0.05,
                    main = "Gene dendrogram and module colors")
dev.off()

```

# 5. Save RData for other analysis.

```{r}
moduleLabels_dis = net_dis$colors
labels2colors(unique(net_dis$colors))

moduleColors_dis = labels2colors(net_dis$colors)

MEs_dis = net_dis$MEs;
geneTree_dis = net_dis$dendrograms[[1]];
save(net_dis,MEs_dis, moduleLabels_dis, moduleColors_dis, geneTree_dis, 
     file = paste0(output,"RData/",study_dis,"-02-networkConstruction-auto.RData"))
```


# 6. Calculation of module preservation in validation cohort

```{r}
setLabels;shortLabels
lnames
multiExpr_preservation = list(discovery = list(data = multiExpr[[1]]$data), validation = list(data = multiExpr[[2]]$data));
multiColor = list(discovery = moduleColors_dis);


system.time( {
  mp = modulePreservation(multiExpr_preservation, multiColor,
                          networkType = "unsigned",
                          referenceNetworks = 1,
                          nPermutations = 1000,
                          maxModuleSize=1500,
                          maxGoldModuleSize=500,
                          randomSeed = 1,
                          quickCor = 0,
                          verbose = 3,
                          parallelCalculation = T)
} );
# Save the results
save(mp, file =  paste0(output,"RData/",study,"-modulePreservation.RData"))

load(paste0(output,"RData/",study,"-modulePreservation.RData"))
```

# 7. Analysis and display of module preservation results

```{r}
discovery = 1
validation = 2
statsObs = cbind(mp$quality$observed[[discovery]][[validation]][, -1], mp$preservation$observed[[discovery]][[validation]][, -1])
statsZ = cbind(mp$quality$Z[[discovery]][[validation]][, -1], mp$preservation$Z[[discovery]][[validation]][, -1]);


# Compare preservation to quality:
print( cbind(statsObs[, c("medianRank.pres", "medianRank.qual")],
             signif(statsZ[, c("Zsummary.pres", "Zsummary.qual")], 2)) )



# Module labels and module sizes are also contained in the results
modColors = rownames(mp$preservation$observed[[discovery]][[validation]])
moduleSizes = mp$preservation$Z[[discovery]][[validation]][, 1];

# leave grey and gold modules out
plotMods = !(modColors %in% c("grey", "gold"));
# Text labels for points
text = modColors[plotMods];

plotMods = !(modColors %in% c(NA));
text = modColors
# Auxiliary convenience variable
plotData = cbind(mp$preservation$observed[[discovery]][[validation]][, 2], mp$preservation$Z[[discovery]][[validation]][, 2])
# Main titles for the plot
mains = c("Preservation Median rank", "Preservation Zsummary");
# Start the plot
sizeGrWindow(10, 5);
jpeg(file = paste0(output_figures,study,"-modulePreservation.jpeg"), wi = 12, he = 9,units = 'in', res = 480)
par(mfrow = c(1,2),mar = c(4.5,4.5,2.5,1))
for (p in 1:2)
{
  min = min(plotData[, p], na.rm = TRUE);
  max = max(plotData[, p], na.rm = TRUE);
  # Adjust ploting ranges appropriately
  if (p==2)
  {
    if (min > -max/10) min = -max/10
    ylim = c(min - 0.1 * (max-min), max + 0.1 * (max-min))
  } else
    ylim = c(max + 0.1 * (max-min), min - 0.1 * (max-min))
  plot(moduleSizes[plotMods], plotData[plotMods, p], col = 1, bg = modColors[plotMods], pch = 21,
       main = mains[p],
       cex = 2.4,
       ylab = mains[p], xlab = "Module size", log = "x",
       ylim = ylim,
       xlim = c(10, 2000), cex.lab = 1.2, cex.axis = 1.2, cex.main =1.4)
  labelPoints(moduleSizes[plotMods], plotData[plotMods, p], text, cex = 1, offs =0.08 ,protectEdges =F);
  # For Zsummary, add threshold lines
  if (p==2)
  {
    abline(h=0)
    abline(h=2, col = "blue", lty = 2)
    abline(h=10, col = "darkgreen", lty = 2)
  }
}
dev.off()
```













